---
title: "1/f Noise Project Manuscript 1 Final Analysis\n"
subtitle: "Fine-Scale Spatial Heterogeneity in Phytochemistry Increases Herbivore Performance by Enhancing Herbivore Foraging"
author: "Vincent S. Pan, Enakshi Ghosh, Paul J. Ode, William C. Wetzel, Kadeem J. Gilbert, Ian S. Pearse"
date: "`r format(Sys.time(), '%B %d, %Y')`"
output: 
  html_document:
    toc_float: true
    toc: true 
    toc_depth: 2 
    number_sections: true
    code_folding: show
    highlight: tango
    theme: default
---

# Setup {.tabset}

```{r include=FALSE}
knitr::opts_chunk$set(
  eval = TRUE, 
  warning = FALSE, 
  message = FALSE, 
  comment = NA
)
```

## Load libraries

```{r, message=FALSE, warning=FALSE}
library(survival)
library(piecewiseSEM)
source("spat1f/init_analysis.R")
```

## Handy functions not in spat1f

```{r}
trend_by_pre_wt <- function(model, term){
  emmeans::emtrends(model, var = "cat_pre_wt_log_scale", specs = term) %>% 
  pairs()
}

contrast_by_pre_wt <- function(model, term, type = c("pairwise", "trt.vs.ctrl"), at = c(-2, 2)){
  type <- match.arg(type)
  f <- as.formula(sprintf("%s ~ %s | cat_pre_wt_log_scale", type, term))
  emmeans::emmeans(model, 
                 f, 
                 var = term, 
                 at = list(cat_pre_wt_log_scale = at))
}

check_mod <- function(model){
 DHARMa::simulateResiduals(model) %>% 
    plot()
  performance::posterior_predictive_check(model)
}


```



## Quick cleaning

```{r}
# Main data.frame for analyses
d <- ref_data %>% 
  filter(error == 0) %>% 
  mutate(
    cat_pre_wt_log = log(cat_pre_wt),
    cat_pre_wt_log_scale = as.numeric(scale(log(cat_pre_wt))),
    cat_size = ifelse(cat_pre_wt < median(cat_pre_wt), "small", "big"),
    has_var = ifelse(var_trt != "constant", 1, 0),
    mean_toxic_conc_scale = as.numeric(scale(mean_toxic_conc)),
    mean_toxic_scale = as.numeric(scale(mean_toxic)),
    area_herb_log_scale = as.numeric(scale(log(area_herb+1))),
    var_toxic_12_scale = as.numeric(scale(var_toxic_12)),
    on_toxic_logit_scale = as.numeric(scale(adjust_prop(on_toxic, 
                                                        trans = "emp", 
                                                        nudge.method = "none", 
                                                        na.action = "ignore"))),
    ava_qual_scale = as.numeric(scale(ava_qual)),
    ava_qual_logit_scale = as.numeric(scale(adjust_prop(ava_qual, 
                                                        trans = "emp", 
                                                        nudge.method = "none", 
                                                        na.action = "ignore"))),
    sl_mean_obs_log_scale = as.numeric(scale(log(sl_mean_obs))),
    cat_pre_wt_log_scale_sq = as.numeric(scale(log(cat_pre_wt)^2)),
    RGR_scale = as.numeric(scale(RGR)), 
    sl_mean_pred1 = shape_1 * scale_1,
    sl_mean_pred2 = shape_2 * scale_2,
    sl_mean_pred3 = shape_3 * scale_3,
    sl_mean_pred4 = shape_4 * scale_4,
    k1 = scale_1 / scale_2,
    k2 = scale_3 / scale_4,
    prop_explore_logit = qlogis(prop_explore),
    prop_explore_logit_scale = as.numeric(scale(prop_explore_logit))
  )

# Subset of data.frame for SEM
d2 <- d %>% 
  filter(
    var_trt != "constant"
  ) %>% 
  filter(
    !is.na(area_herb_log_scale) & 
      !is.na(var_toxic_12_scale) & 
      !is.na(mean_toxic_conc_scale) &
      !is.na(sl_mean_obs) &
      !is.na(prop_explore) & 
      !is.na(RGR)) %>% 
  mutate(
    var_high = ifelse(var_trt == "high_var", 1, 0),
    beta_red = ifelse(as.character(beta) == 5, 1, 0),
    beta_white = ifelse(as.character(beta) == 0, 1, 0),
    beta_red_cat_pre_wt_log_scale = beta_red * cat_pre_wt_log_scale,
    beta_white_cat_pre_wt_log_scale = beta_white * cat_pre_wt_log_scale,
    var_high_cat_pre_wt_log_scale = var_high * cat_pre_wt_log_scale,
    beta_numeric_scale = as.numeric(scale(as.numeric(beta)))
  )

# Subset of data.frame for more detailed analyses
d3 <- d %>% 
  filter(
    var_trt != "constant"
  ) %>% 
  filter_at(vars(contains("shape_"), contains("scale_[0-9]"), contains("sl_mean_pred")), 
            all_vars(. > 0)) %>% 
  filter(sl_mean_pred2 < 2000) %>% 
  mutate(
    var_high = ifelse(var_trt == "high_var", 1, 0),
    beta_red = ifelse(as.character(beta) == 5, 1, 0),
    beta_white = ifelse(as.character(beta) == 0, 1, 0),
    beta_red_cat_pre_wt_log_scale = beta_red * cat_pre_wt_log_scale,
    beta_white_cat_pre_wt_log_scale = beta_white * cat_pre_wt_log_scale,
    var_high_cat_pre_wt_log_scale = var_high * cat_pre_wt_log_scale,
    beta_numeric_scale = as.numeric(scale(as.numeric(beta)))
  )
```



# Herbivore Performance

## RGR {.tabset}

### Model summary
```{r}
rgr_m <- glmmTMB(
  RGR ~ 
    (var_trt + beta) * cat_pre_wt_log_scale +
    I(cat_pre_wt_log_scale^2) +  # residual plot show significant non-linearity
    (1|session_id),
  data = d %>% 
    filter(
      var_trt != "constant"
    ) 
); summary(rgr_m)


car::Anova(rgr_m, type = "III")

```

### Post-hoc contrasts

```{r}
trend_by_pre_wt(rgr_m, "var_trt")
contrast_by_pre_wt(rgr_m, "var_trt")

trend_by_pre_wt(rgr_m, "beta")
contrast_by_pre_wt(rgr_m, "beta")
```


### Misc stats
```{r}
r2(rgr_m, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(rgr_m)
```


### Plot
```{r}
g1 <- marginal_effects(rgr_m, terms = c("cat_pre_wt_log_scale","beta")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = yhat)) + 
  geom_ribbon(aes(ymax = upper, ymin = lower, fill = beta), alpha = 0.2) + 
  geom_line(aes(color = beta), linewidth = 2) + 
  geom_point(
    data = rgr_m$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = RGR, color = beta),
    size = 3, alpha = 0.8
  ) + 
  theme_bw(base_size = 15) + 
  theme(legend.position = "top") +
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  scale_color_brewer(type = "qual", aesthetics = c("fill","color")) + 
  labs(x = "Cat pre-weight (g)", y = expression(RGR~(hour^-1)),
       color = expression(beta), fill = expression(beta))

g2 <- marginal_effects(rgr_m, terms = c("cat_pre_wt_log_scale","var_trt")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = yhat)) + 
  geom_ribbon(aes(ymax = upper, ymin = lower, fill = var_trt), alpha = 0.2) + 
  geom_line(aes(color = var_trt), linewidth = 2) + 
  geom_point(
    data = rgr_m$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = RGR, color = var_trt),
    size = 3, alpha = 0.8
  ) + 
  theme_bw(base_size = 15) + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  theme(legend.position = "top") +
  scale_color_discrete(type = c("navy","skyblue"), 
                       aesthetics = c("fill","color"), 
                       label = c("High", "Low")) + 
  labs(x = "Cat pre-weight (g)", y = expression(RGR~(hour^-1)),
       color = "Variation", fill = "Variation")


ggarrange(g1, g2 + labs(y = ""))
```


## Time to pupation {.tabset}

### Model summary
```{r}
pupt_m_full <- glmmTMB(
  time_to_pupation ~ 
    (var_trt + beta) * cat_pre_wt_log_scale + 
    I(cat_pre_wt_log_scale^2) + # Residuals show significant non-linearity
    (1|session_id),
  data = d %>% 
    filter(var_trt != "constant"), 
  family = Gamma(link = "log"),
); summary(pupt_m_full)

car::Anova(pupt_m_full, type = "III")

pupt_m <- glmmTMB(
  time_to_pupation ~ 
    var_trt + beta * cat_pre_wt_log_scale + 
    I(cat_pre_wt_log_scale^2) + # Residuals show significant non-linearity
    (1|session_id),
  data = d %>% 
    filter(var_trt != "constant"), 
  family = Gamma(link = "log"),
); summary(pupt_m)

car::Anova(pupt_m, type = "III")



```

### Post-hoc contrasts

```{r}
contrast_by_pre_wt(pupt_m, "var_trt")

trend_by_pre_wt(pupt_m, "beta")
contrast_by_pre_wt(pupt_m, "beta")
```


### Misc stats
```{r}
r2(pupt_m, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(pupt_m)
```


### Plot
```{r}
g3 <- marginal_effects(pupt_m, terms = c("cat_pre_wt_log_scale","beta")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = yhat)) + 
  geom_ribbon(aes(ymax = upper, ymin = lower, fill = beta), alpha = 0.2) + 
  geom_line(aes(color = beta), linewidth = 2) + 
  geom_point(
    data = pupt_m$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = time_to_pupation, color = beta),
    size = 3, alpha = 0.8
  ) + 
  theme_bw(base_size = 15) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log2") +
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  scale_color_brewer(type = "qual", aesthetics = c("fill","color")) + 
  labs(x = "Cat pre-weight (g)", y = "Time to pupation (days)",
       color = expression(beta), fill = expression(beta))

g4 <- marginal_effects(pupt_m, terms = c("var_trt")) %>% 
  ggplot(aes(x = var_trt, y = yhat)) + 
  geom_point(
    data = pupt_m$frame,
    aes(x = var_trt, y = time_to_pupation, color = var_trt),
    position = position_jitter(width = 0.2),
    size = 3, alpha = 0.8
  ) + 
  geom_pointrange(
    aes(ymax = upper, ymin = lower), 
    color = "black",
    size = 1, linewidth = 2, shape = 1,
  ) +
  theme_bw(base_size = 15) + 
  scale_y_continuous(trans = "log2") +
  theme(legend.position = "top") +
  scale_color_discrete(type = c("navy","skyblue"), 
                       aesthetics = c("color"), 
                       label = c("High", "Low")) + 
  labs(x = "Variation", y = "Time to pupation (days)",
       color = "Variation")


ggarrange(g3, g4 + labs(y = ""))
```

## Eclosure {.tabset}

### Model summary
```{r}
eclosure_m_full <- glmmTMB(
  eclosed ~ 
    (var_trt + beta) * cat_pre_wt_log_scale + 
    (1|session_id),
  data = d %>% 
    filter(var_trt != "constant"), 
  family = binomial(link = "logit"),
); summary(eclosure_m_full)

car::Anova(eclosure_m_full, type = "III")

eclosure_m <- glmmTMB(
  eclosed ~ 
    (var_trt + beta) + cat_pre_wt_log_scale + 
    (1|session_id),
  data = d %>% 
    filter(var_trt != "constant"), 
  family = binomial(link = "logit"),
); summary(eclosure_m)

car::Anova(eclosure_m, type = "II")



```

### Post-hoc contrasts

```{r}

```


### Misc stats
```{r}
r2(eclosure_m, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(eclosure_m)
```


### Plot
```{r}

```



## Survival {.tabset}

### Model summary
```{r}
surv_m_full <- coxph(
  Surv(surv_time, observed_dead) ~ 
    (var_trt + beta) * cat_pre_wt_log_scale + I(cat_pre_wt_log_scale^2) +
    strata(session_id),
  data = d %>% 
    filter(var_trt != "constant") %>% 
    mutate(
      beta = as.factor(as.character(beta))
    ),
); summary(surv_m_full)

drop1(surv_m_full, test = "Chisq")

surv_m <- coxph(
  Surv(surv_time, observed_dead) ~ 
    (var_trt + beta) + cat_pre_wt_log_scale + I(cat_pre_wt_log_scale^2) + 
    strata(session_id),
  data = d %>% 
    filter(var_trt != "constant") %>% 
    mutate(
      beta = as.factor(as.character(beta))
    ),
); summary(surv_m)

drop1(surv_m, test = "Chisq")



```

### Post-hoc contrasts

```{r}

```


### Misc stats
```{r}
r2(surv_m, tolerance = 10^-10)
```


### Check model
```{r}
cox.zph(surv_m)
```


### Plot
```{r}

```




# Structural Equation Model

## Sub-models {.tabset}

### RGR

```{r}
subm_rgr <- glmmTMB(
  RGR_scale ~ 
    cat_pre_wt_log_scale + 
    cat_pre_wt_log_scale_sq + 
    sl_mean_obs_log_scale +
    prop_explore_logit_scale *  
    var_toxic_12_scale + 
    mean_toxic_conc_scale + 
    area_herb_log_scale + 
    beta_numeric_scale + 
    (1|session_id),
  data = d2
); summary(subm_rgr)
```


### Variance in toxin (12 hour)

```{r}
subm_var_toxic <- glmmTMB(
  var_toxic_12_scale ~ 
    sl_mean_obs_log_scale +
    beta_numeric_scale + 
    var_high + 
    (1|session_id),
  data = d2
); summary(subm_var_toxic)

```


### Mean step length

```{r}
subm_sl <- glmmTMB(
  sl_mean_obs_log_scale ~ 
    prop_explore_logit_scale +  
    cat_pre_wt_log_scale + 
    cat_pre_wt_log_scale_sq + 
    on_toxic_logit_scale + 
    (1|session_id),
  data = d2,
); summary(subm_sl)

```


### Mean toxin ingested

```{r}
subm_toxin_ingested <- glmmTMB(
  mean_toxic_conc_scale ~ 
    beta_numeric_scale + 
    on_toxic_logit_scale + 
    var_high + 
    (1|session_id),
  data = d2 
); summary(subm_toxin_ingested)

```


### Mean time on toxin

```{r}
subm_on_toxic <- glmmTMB(
  on_toxic_logit_scale ~ 
    var_high + beta_numeric_scale * cat_pre_wt_log_scale + 
    (1|session_id),
  family = gaussian(),
  data = d2
); summary(subm_on_toxic)

```


### Area consumption

```{r}
subm_herb <- glmmTMB(
  area_herb_log_scale ~ 
    var_high * cat_pre_wt_log_scale +
    (1|session_id),
  data = d2,
); summary(subm_herb)

```

### Exploration
```{r}
subm_exp <- glmmTMB(
  prop_explore_logit_scale ~ 
    var_high + beta_numeric_scale * cat_pre_wt_log_scale + 
    (1|session_id),
  family = gaussian(),
  data = d2
); summary(subm_exp)

```



## d-separation test

```{r echo=TRUE, message=FALSE, warning=FALSE, include=TRUE}
sem_fit <- psem(
    subm_rgr,
    subm_herb,
    subm_var_toxic,
    subm_on_toxic,
    subm_toxin_ingested,
    subm_exp,
    subm_sl, 
    var_toxic_12_scale %~~% on_toxic_logit_scale, # correlated errors
    data = d2
)
sem_summary <- suppressWarnings(suppressMessages(
  summary_psem(sem_fit, 
               no_standardize_x =  c(), 
               .progressBar = FALSE, 
               direction = "var_toxic_12_scale -> area_herb_log_scale")
))

```

```{r}
sem_summary$Cstat
```


```{r}
knitr::kable(sem_summary$dTable)
```

## Model summary {.tabset}

### Model stats

```{r}
sem_summary$ChiSq
sem_summary$AIC
sem_summary$R2
```

### Standardized coefficients
```{r}
knitr::kable(
  cbind(sem_summary$coefficients,"arrow_size"=(abs(as.numeric(sem_summary$coefficients$Std.Estimate))*20))
)
```

### Post hoc contrast


```{r}
contrast_by_pre_wt(subm_herb, "var_high", "trt")
sd(subm_herb$frame$var_high)/sd(subm_herb$frame$area_herb_log_scale)
```



```{r}
emmeans::emtrends(subm_exp, 
                 ~ beta_numeric_scale | cat_pre_wt_log_scale, 
                 var = "beta_numeric_scale", 
                 at = list(cat_pre_wt_log_scale = c(-2,2)))
sd(subm_exp$frame$beta_numeric_scale) * sd(subm_exp$frame$prop_explore_logit_scale)
```

```{r}
emmeans::emtrends(subm_on_toxic, 
                 ~ beta_numeric_scale | cat_pre_wt_log_scale, 
                 var = "beta_numeric_scale", 
                 at = list(cat_pre_wt_log_scale = c(-2,2)))
sd(subm_on_toxic$frame$beta_numeric_scale) * sd(subm_on_toxic$frame$on_toxic_logit_scale)
```

## SEM plots


```{r}
knitr::include_graphics(paste0(getwd(), "/graphs/manuscript1_figures/SEM_simplified.png"), rel_path = FALSE)
```


# ISSF parameters

## Selection strength state 1 {.tabset}

### Model summary
```{r}
m_select_s1_full <- glmmTMB(
  s1.less_toxic.est ~ 
    cat_pre_wt_log_scale * (beta + var_trt) + 
    (1|session_id),
  data = d3,
); summary(m_select_s1_full)

m_select_s1 <- glmmTMB(
  s1.less_toxic.est ~ 
    cat_pre_wt_log_scale + beta + var_trt + 
    (1|session_id),
  data = d3,
); summary(m_select_s1)

```

### Post-hoc contrasts

```{r}
contrast_by_pre_wt(m_select_s1, "cat_pre_wt_log_scale")
```


### Misc stats
```{r}
r2(m_select_s1, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(m_select_s1)
```


### Plot
```{r}
marginal_effects(m_select_s1, terms = c("cat_pre_wt_log_scale")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = exp(yhat))) + 
  geom_hline(aes(yintercept = 1), color = "tomato", linetype = "dashed", linewidth = 1) + 
  geom_ribbon(aes(ymax = exp(upper), ymin = exp(lower)), alpha = 0.2) + 
  geom_line(linewidth = 2) + 
  geom_point(
    data = m_select_s1$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = exp(s1.less_toxic.est)),
    size = 3, alpha = 0.8
  ) +  
  theme_bw(base_size = 15) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log10", breaks = c(0.5, 2, 1)) + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  labs(x = "Cat pre-weight (g)", y = "Less toxic diet selection strength (odds ratio)")
```


## Selection strength state 2 {.tabset}

### Model summary
```{r}
m_select_s2_full <- glmmTMB(
  s2.less_toxic.est ~ 
    cat_pre_wt_log_scale * (beta + var_trt) + 
    (1|session_id),
  data = d3,
); summary(m_select_s2_full)

m_select_s2 <- glmmTMB(
  s2.less_toxic.est ~ 
    cat_pre_wt_log_scale + beta + var_trt + 
    (1|session_id),
  data = d3,
); summary(m_select_s2)

```

### Post-hoc contrasts

```{r}

```


### Misc stats
```{r}
r2(m_select_s2, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(m_select_s2)
```


### Plot
```{r}
marginal_effects(m_select_s2, terms = c("cat_pre_wt_log_scale")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = exp(yhat))) + 
  geom_hline(aes(yintercept = 1), color = "tomato", linetype = "dashed", linewidth = 1) + 
  geom_ribbon(aes(ymax = exp(upper), ymin = exp(lower)), alpha = 0.2) + 
  geom_line(linewidth = 2) + 
  geom_point(
    data = m_select_s2$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = exp(s2.less_toxic.est)),
    size = 3, alpha = 0.8
  ) +  
  theme_bw(base_size = 15) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log10", breaks = c(0.5, 2, 1)) + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  labs(x = "Cat pre-weight (g)", y = "Less toxic diet selection strength (odds ratio)")
```




## Arrestment state 1 {.tabset}

### Model summary
```{r}
m_arrest_s1_full <- glmmTMB(
  log(k1) ~ 
    cat_pre_wt_log_scale * (beta + var_trt) + 
    (1|session_id),
  data = d3,
); summary(m_arrest_s1_full)

m_arrest_s1 <- glmmTMB(
  log(k1) ~ 
    cat_pre_wt_log_scale * beta + var_trt + 
    (1|session_id),
  data = d3,
); summary(m_arrest_s1)

```

### Post-hoc contrasts

```{r}
contrast_by_pre_wt(m_arrest_s1, "beta")
```


### Misc stats
```{r}
r2(m_arrest_s1, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(m_arrest_s1)
```


### Plot
```{r}
marginal_effects(m_arrest_s1, terms = c("cat_pre_wt_log_scale", "beta")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = (yhat), color = beta)) + 
  geom_ribbon(aes(ymax = (upper), ymin = lower, fill = beta, color = NULL), alpha = 0.2) + 
  geom_line(linewidth = 2) + 
  geom_point(
    data = m_arrest_s1$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = exp(`log(k1)`)),
    size = 3, alpha = 0.5
  ) +  
  theme_bw(base_size = 15) + 
    geom_hline(aes(yintercept = 1), color = "black", linetype = "dashed", linewidth = 1) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log10") + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  scale_color_brewer(type = "qual", aesthetics = c("color","fill")) + 
  labs(x = "Cat pre-weight (g)", y = "Less toxic diet arresetment strength (ratio)", 
       color = expression(beta), fill = expression(beta))
```






## Arrestment state 2 {.tabset}

### Model summary
```{r}
m_arrest_s2_full <- glmmTMB(
  log(k2) ~ 
    cat_pre_wt_log_scale * (beta + var_trt) + 
    (1|session_id),
  data = d3,
); summary(m_arrest_s2_full)

m_arrest_s2 <- glmmTMB(
  log(k2) ~ 
    cat_pre_wt_log_scale + beta + var_trt + 
    (1|session_id),
  data = d3,
); summary(m_arrest_s2)

```

### Post-hoc contrasts

```{r}

```


### Misc stats
```{r}
r2(m_arrest_s2, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(m_arrest_s2)
```


### Plot
```{r}
marginal_effects(m_arrest_s2, terms = c("cat_pre_wt_log_scale", "beta")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = (yhat), color = beta)) + 
  geom_ribbon(aes(ymax = (upper), ymin = lower, fill = beta, color = NULL), alpha = 0.2) + 
  geom_line(linewidth = 2) + 
  geom_point(
    data = m_arrest_s2$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = exp(`log(k2)`)),
    size = 3, alpha = 0.5
  ) +  
  theme_bw(base_size = 15) + 
    geom_hline(aes(yintercept = 1), color = "black", linetype = "dashed", linewidth = 1) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log10") + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  scale_color_brewer(type = "qual", aesthetics = c("color","fill")) + 
  labs(x = "Cat pre-weight (g)", y = "Less toxic diet arresetment strength (ratio)", 
       color = expression(beta), fill = expression(beta))
```




## Toxic diet step length state 1 {.tabset}

### Model summary
```{r}
m_sl_pred_s1_full <- glmmTMB(
  log(sl_mean_pred1) ~ 
    cat_pre_wt_log_scale * (beta + var_trt) + 
    (1|session_id),
  data = d3,
); summary(m_sl_pred_s1_full)

m_sl_pred_s1 <- glmmTMB(
  log(sl_mean_pred1) ~ 
    cat_pre_wt_log_scale + beta + var_trt + 
    (1|session_id),
  data = d3,
); summary(m_sl_pred_s1)

```

### Post-hoc contrasts

```{r}

```


### Misc stats
```{r}
r2(m_sl_pred_s1, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(m_sl_pred_s1)
```


### Plot
```{r}
marginal_effects(m_sl_pred_s1, terms = c("cat_pre_wt_log_scale")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = (yhat) / 1000 * 12)) + 
  geom_ribbon(aes(ymax = (upper)/ 1000 * 12, ymin = lower/ 1000 * 12), alpha = 0.2) + 
  geom_line(linewidth = 2) + 
  geom_point(
    data = m_sl_pred_s1$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), 
        y = exp(`log(sl_mean_pred1)`) / 1000 * 12),
    size = 3, alpha = 0.5
  ) +  
  theme_bw(base_size = 15) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log10", labels = fancy_scientific) + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  scale_color_brewer(type = "qual", aesthetics = c("color","fill")) + 
  labs(x = "Cat pre-weight (g)", y = "Selection free step length \non toxic diet (cm)")
```




## Toxic diet step length state 2 {.tabset}

### Model summary
```{r}
m_sl_pred_s2_full <- glmmTMB(
  log(sl_mean_pred3) ~ 
    cat_pre_wt_log_scale * (beta + var_trt) + 
    (1|session_id),
  data = d3,
); summary(m_sl_pred_s2_full)

m_sl_pred_s2 <- glmmTMB(
  log(sl_mean_pred3) ~ 
    cat_pre_wt_log_scale + beta + var_trt + 
    (1|session_id),
  data = d3,
); summary(m_sl_pred_s2)

```

### Post-hoc contrasts

```{r}

```


### Misc stats
```{r}
r2(m_sl_pred_s2, tolerance = 10^-10)
```


### Check model
```{r}
check_mod(m_sl_pred_s2)
```


### Plot
```{r}
marginal_effects(m_sl_pred_s2, terms = c("cat_pre_wt_log_scale")) %>% 
  ggplot(aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), y = (yhat) / 1000 * 12)) + 
  geom_ribbon(aes(ymax = (upper)/ 1000 * 12, ymin = lower/ 1000 * 12), alpha = 0.2) + 
  geom_line(linewidth = 2) + 
  geom_point(
    data = m_sl_pred_s2$frame,
    aes(x = unscalelog(d$cat_pre_wt_log)(cat_pre_wt_log_scale), 
        y = exp(`log(sl_mean_pred3)`) / 1000 * 12),
    size = 3, alpha = 0.5
  ) +  
  theme_bw(base_size = 15) + 
  theme(legend.position = "top") +
  scale_y_continuous(trans = "log10") + 
  scale_x_continuous(trans = "log10", labels = fancy_scientific) +
  scale_color_brewer(type = "qual", aesthetics = c("color","fill")) + 
  labs(x = "Cat pre-weight (g)", y = "Selection free step length \non toxic diet (cm)")
```




# Session Info

```{r}
sessionInfo()
```

